Visualization

### 2023-01-26 Code/NewPlots.Rmd
Manuscript Update

```{r}
graph_bts <- function(cov, theta, target, width, nrep = 1000, sizes = c(100, 500, 1000), types = c('estCI', 'mbtCI', 'altCI', 'bcaCIest', 'bcaCImbt', 'bcaCIalt'), parameters = c('mu', 'sigma', 'theta'), level = .95) {
  n <- rep(sizes, each = length(types) * length(parameters))
  CI <- rep(types, times = length(sizes), each = length(parameters))
  t <- rep(parameters, times = length(sizes) * length(types))
  LB <- sapply(cov, function(i) prop.test(i*nrep, nrep)$conf.int[1])
  UB <-sapply(cov, function(i) prop.test(i*nrep, nrep)$conf.int[2])

@@

```{r}
theta <- 0.1
target <- c(0, 1, theta)
cov <- c(mychk(sim_.1_1h, target), mychk(sim_.1_5h, target), mychk(sim_.1_1k, target))

graph_bts(cov, theta, target, width = 50)
ggsave('../Manuscript/plot_.1.pdf')
```
```{r}
theta <- 0.3
target <- c(0, 1, theta)
cov <- c(mychk(sim_.3_1h, target), mychk(sim_.3_5h, target), mychk(sim_.3_1k, target))

graph_bts(cov, theta, target, width = 25)
ggsave('../Manuscript/plot_.3.pdf')
```
```{r}
theta <- 0.5
target <- c(0, 1, theta)
cov <- c(mychk(sim_.5_1h, target), mychk(sim_.5_5h, target), mychk(sim_.5_1k, target))

graph_bts(cov, theta, target, width = 10)
ggsave('../Manuscript/plot_.5.pdf')
```

>>>>

```{r}
graph_bts <- function(cov, phi, target, width, nrep = 1000, sizes = c(100, 200, 300, 400, 500), types = c('estCI', 'mbtCI', 'altCI', 'bcaCIest', 'bcaCImbt', 'bcaCIalt'), parameters = c('mu', 'sigma', 'phi'), level = .95) {
  n <- rep(sizes, each = length(types) * length(parameters))
  CI <- rep(types, times = length(sizes), each = length(parameters))
  t <- rep(parameters, times = length(sizes) * length(types))
  LB <- sapply(cov, function(i) prop.test(i*nrep, nrep)$conf.int[1])
  UB <-sapply(cov, function(i) prop.test(i*nrep, nrep)$conf.int[2])

@@

```{r}
phi <- 0
target <- c(0, 1, phi)
cov <- c(mychk(sim_0_1h, target), mychk(sim_0_2h, target), mychk(sim_0_3h, target), mychk(sim_0_4h, target), mychk(sim_0_5h, target))
graph_bts(cov, phi, target, width = 25)
ggsave('../Manuscript/figures/plot_0.pdf')
```
```{r}
phi <- .2
target <- c(0, 1, phi)
cov <- c(mychk(sim_.2_1h, target), mychk(sim_.2_2h, target), mychk(sim_.2_3h, target), mychk(sim_.2_4h, target), mychk(sim_.2_5h, target))
graph_bts(cov, phi, target, width = 25)
ggsave('../Manuscript/figures/plot_.2.pdf')
```
```{r}
phi <- .4
target <- c(0, 1, phi)
cov <- c(mychk(sim_.4_1h, target), mychk(sim_.4_2h, target), mychk(sim_.4_3h, target), mychk(sim_.4_4h, target), mychk(sim_.4_5h, target))

graph_bts(cov, phi, target, width = 10)
ggsave('../Manuscript/figures/plot_.4.pdf')
```

### 2023-01-26 Code/simulation.Rmd
Manuscript Update

do1rep <- function(n, theta, statistic, blksize, R = 1000, level = .95) {
    x <- arima.sim(list(ar = theta), n = n) * sqrt(1 - theta^2)
    bts <- boot::tsboot(x, statistic, l = blksize, sim = "fixed", R = R)
    alpha <- 1 - level

@@

```{r ma = .1, n = 100}
n <- 100
blksize <- 5
theta <- .1
target <- c(0, 1, theta)
set.seed(1234)
sim_.1_1h <- replicate(nrep, do1rep(n, theta, mystat, blksize))
write.csv(sim_.1_1h,"../Data/Raw/sim_.1_1h.csv", row.names = FALSE)
mychk(sim_.1_1h, target)
```
```{r ma = .1, n = 500}
n <- 500
blksize <- 8
theta <- .1
target <- c(0, 1, theta)
set.seed(2345)
sim_.1_5h <- replicate(nrep, do1rep(n, theta, mystat, blksize))
write.csv(sim_.1_5h,"../Data/Raw/sim_.1_5h.csv", row.names = FALSE)
mychk(sim_.1_5h, target)
```
```{r ma = .1, n = 1000}
n <- 1000
blksize <- 10
theta <- .1
target <- c(0, 1, theta)
set.seed(3456)
sim_.1_1k <- replicate(nrep, do1rep(n, theta, mystat, blksize))
write.csv(sim_.1_1k,"../Data/Raw/sim_.1_1k.csv", row.names = FALSE)
mychk(sim_.1_1k, target)
```
```{r ma = .3, n = 100}
n <- 100
blksize <- 5
theta <- .3
target <- c(0, 1, theta)
set.seed(1234)
sim_.3_1h <- replicate(nrep, do1rep(n, theta, mystat, blksize))
write.csv(sim_.3_1h,"../Data/Raw/sim_.3_1h.csv", row.names = FALSE)
mychk(sim_.3_1h, target)
```
```{r ma = .3, n = 500}
n <- 500
blksize <- 8
theta <- .3
target <- c(0, 1, theta)
set.seed(2345)
sim_.3_5h <- replicate(nrep, do1rep(n, theta, mystat, blksize))
write.csv(sim_.3_5h,"../Data/Raw/sim_.3_5h.csv", row.names = FALSE)
mychk(sim_.3_5h, target)
```
```{r ma = .3, n = 1000}
n <- 1000
blksize <- 10
theta <- .3
target <- c(0, 1, theta)
set.seed(3456)
sim_.3_1k <- replicate(nrep, do1rep(n, theta, mystat, blksize))
write.csv(sim_.3_1k,"../Data/Raw/sim_.3_1k.csv", row.names = FALSE)
mychk(sim_.3_1k, target)
```
```{r ma = .5, n = 100}
n <- 100
blksize <- 5
theta <- .5
target <- c(0, 1, theta)
set.seed(1234)
sim_.5_1h <- replicate(nrep, do1rep(n, theta, mystat, blksize))
write.csv(sim_.5_1h,"../Data/Raw/sim_.5_1h.csv", row.names = FALSE)
mychk(sim_.5_1h, target)
```
```{r ma = .5, n = 500}
n <- 500
blksize <- 8
theta <- .5
target <- c(0, 1, theta)
set.seed(2345)
sim_.5_5h <- replicate(nrep, do1rep(n, theta, mystat, blksize))
write.csv(sim_.5_5h,"../Data/Raw/sim_.5_5h.csv", row.names = FALSE)
mychk(sim_.5_5h, target)
```
```{r ma = .5, n = 1000}
n <- 1000
blksize <- 10
theta <- .5
target <- c(0, 1, theta)
set.seed(3456)
sim_.5_1k <- replicate(nrep, do1rep(n, theta, mystat, blksize))
write.csv(sim_.5_1k,"../Data/Raw/sim_.5_1k.csv", row.names = FALSE)
mychk(sim_.5_1k, target)
```

>>>>

do1rep <- function(n, phi, statistic, blksize, R = 1000, level = .95) {
    if (phi == 0) {
      x <- rnorm(n)
    }
    else {
      x <- arima.sim(list(ar = phi), n = n) * sqrt(1 - phi^2)
    }
    bts <- boot::tsboot(x, statistic, l = blksize, sim = "fixed", R = R)
    alpha <- 1 - level

@@

```{r ar = 0, n = 100}
n <- 100
blksize <- 5
phi <- 0
target <- c(0, 1, phi)
set.seed(1234)
sim_0_1h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
write.csv(sim_0_1h,"../Data/Raw/sim_0_1h.csv", row.names = FALSE)
mychk(sim_0_1h, target)
```

```{r ar = 0, n = 200}
n <- 200
blksize <- 6
phi <- 0
target <- c(0, 1, phi)
set.seed(2345)
sim_0_2h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
write.csv(sim_0_2h,"../Data/Raw/sim_0_2h.csv", row.names = FALSE)
mychk(sim_0_2h, target)
```

```{r ar = 0, n = 300}
n <- 300
blksize <- 7
phi <- 0
target <- c(0, 1, phi)
set.seed(3456)
sim_0_3h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
write.csv(sim_0_3h,"../Data/Raw/sim_0_3h.csv", row.names = FALSE)
mychk(sim_0_3h, target)
```

```{r ar = 0, n = 400}
n <- 400
blksize <- 7
phi <- 0
target <- c(0, 1, phi)
set.seed(4567)
sim_0_4h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
write.csv(sim_0_4h,"../Data/Raw/sim_0_4h.csv", row.names = FALSE)
mychk(sim_0_4h, target)
```

```{r ar = 0, n = 500}
n <- 500
blksize <- 8
phi <- 0
target <- c(0, 1, phi)
set.seed(5678)
sim_0_5h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
write.csv(sim_0_5h,"../Data/Raw/sim_0_5h.csv", row.names = FALSE)
mychk(sim_0_5h, target)
```

```{r ar = .2, n = 100}
n <- 100
blksize <- 5
phi <- .2
target <- c(0, 1, phi)
set.seed(1234)
sim_.2_1h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
write.csv(sim_.2_1h,"../Data/Raw/sim_.2_1h.csv", row.names = FALSE)
mychk(sim_.2_1h, target)
```

```{r ar = .2, n = 200}
n <- 200
blksize <- 6
phi <- .2
target <- c(0, 1, phi)
set.seed(2345)
sim_.2_2h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
write.csv(sim_.2_2h,"../Data/Raw/sim_.2_2h.csv", row.names = FALSE)
mychk(sim_.2_2h, target)
```

```{r ar = .2, n = 300}
n <- 300
blksize <- 7
phi <- .2
target <- c(0, 1, phi)
set.seed(3456)
sim_.2_3h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
write.csv(sim_.2_3h,"../Data/Raw/sim_.2_3h.csv", row.names = FALSE)
mychk(sim_.2_3h, target)
```

```{r ar = .2, n = 400}
n <- 400
blksize <- 7
phi <- .2
target <- c(0, 1, phi)
set.seed(4567)
sim_.2_4h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
write.csv(sim_.2_4h,"../Data/Raw/sim_.2_4h.csv", row.names = FALSE)
mychk(sim_.2_4h, target)
```

```{r ar = .2, n = 500}
n <- 500
blksize <- 8
phi <- .2
target <- c(0, 1, phi)
set.seed(5678)
sim_.2_5h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
write.csv(sim_.2_5h,"../Data/Raw/sim_.2_5h.csv", row.names = FALSE)
mychk(sim_.2_5h, target)
```

```{r ar = .4, n = 100}
n <- 100
blksize <- 5
phi <- .4
target <- c(0, 1, phi)
set.seed(1234)
sim_.4_1h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
write.csv(sim_.4_1h,"../Data/Raw/sim_.4_1h.csv", row.names = FALSE)
mychk(sim_.4_1h, target)
```

```{r ar = .4, n = 200}
n <- 200
blksize <- 6
phi <- .4
target <- c(0, 1, phi)
set.seed(2345)
sim_.4_2h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
write.csv(sim_.4_2h,"../Data/Raw/sim_.4_2h.csv", row.names = FALSE)
mychk(sim_.4_2h, target)
```

```{r ar = .4, n = 300}
n <- 300
blksize <- 7
phi <- .4
target <- c(0, 1, phi)
set.seed(3456)
sim_.4_3h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
write.csv(sim_.4_3h,"../Data/Raw/sim_.4_3h.csv", row.names = FALSE)
mychk(sim_.4_3h, target)
```

```{r ar = .4, n = 400}
n <- 400
blksize <- 7
phi <- .4
target <- c(0, 1, phi)
set.seed(4567)
sim_.4_4h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
write.csv(sim_.4_4h,"../Data/Raw/sim_.4_4h.csv", row.names = FALSE)
mychk(sim_.4_4h, target)
```

```{r ar = .4, n = 500}
n <- 500
blksize <- 8
phi <- .4
target <- c(0, 1, phi)
set.seed(5678)
sim_.4_5h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
write.csv(sim_.4_5h,"../Data/Raw/sim_.4_5h.csv", row.names = FALSE)
mychk(sim_.4_5h, target)
```
